---
title: "OPM-Delay"
author: "Pete Jones"
date: "03/05/2015"
output: html_document
---

From government workers to bartenders, much of Washington depends on the status of the Federal Government. This chart will help the district know when to look for that all important email. Set your alarm, folks!

```{r}
#set libraries
library(ggplot2)
library(dplyr)
library(knitr)
library(stringr)

#Data comes from @zubakskees gist: https://gist.github.com/chriszs/490d9930ac0421f84857 - slightly modified by me. 12-hr changed to 24 hour times.
opm <- read.csv("opmoperatingstatus.csv", stringsAsFactors=FALSE)

opm$ptime <- strptime(opm$time, format = "%H:%M")

opmtime

qplot(ptime, status, data=opm)

opmplot <- ggplot(data=opm, aes(ptime, year)) + geom_point(aes(color=status)) +scale_colour_manual(values=c("red", "yellow", "green"))
opmplot






```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
